A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-15 EvoPar2017/paper.tex
Adding Twitter example

All experiments are announced in the same way: we use social networks,
mainly Twitter, to announce the start of a new experiment. LinkedIn,
Facebook, and also private groups in Telegram and WhatsApp have been
used for announcements too. We also encourage friends and followers to
put a self-authored post for announcing it, instead of just sharing, in
the way allowed by the platform, our original posts. During the running
of the experiments, users are engaged, questions answered, and all
kind of explanations given if requested. In general, announcements
have been made in Spanish, but in some cases English was used
too. This makes for a certainly unreliable experimentation framework,
but it is a realistic one. The steps in the design of the evolutionary
algorithm will be explained next.

>>>>

All experiments are announced in the same way: we use social networks,
mainly Twitter, to announce the start of a new experiment. LinkedIn,
Facebook, and also private groups in Telegram and WhatsApp have been
used for announcements too. We also encourage friends and followers to
put their own posts for announcing it, instead of just sharing, in
the way allowed by the platform, our original ones. For instance, when using Twitter, to include the URL of the experiment inside a tweet of their own, instead of just sharing it via a re-tweet (RT). During the running
of the experiments, users are engaged, questions answered, and all
kind of explanations given if requested. In general, announcements
have been made in Spanish, but in some cases English was used
too. This makes for a certainly unreliable experimentation framework,
but it is a realistic one. The steps in the design of the evolutionary
algorithm will be explained next.
